---
title: "Analyze ToothGrowth Dataset"
author: "York Huang"
date: "Sunday, March 13, 2016"
output:
  pdf_document:
    fig_height: 3
    fig_width: 4
---
## Overview
In the project, we're going to analyze the ToothGrowth data in the R datasets package

## Prepare Data
Load data from R ToothGrowth package and convert to data frame.
```{r}
library(ggplot2)

data(ToothGrowth)
tg <- data.frame(ToothGrowth)
```

## Exploration Data
There are 60 observations. 
```{r}
dim(tg)
head(tg)
```
Summary of data (tg) -
```{r}
summary(tg)
```
Plot tooth length vs supplement.
```{r}
ggplot(data=tg, aes(x=supp, y=len)) + geom_boxplot(aes(fill=supp))
```
Plot tooth length vs dose.
```{r}
ggplot(data=tg, aes(x=dose, y=len)) + geom_boxplot(aes(fill=factor(dose)))
```

## Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose

Compare between supplements.
```{r}
t.test(tg$len[tg$supp=="OJ"], tg$len[tg$supp=="VC"], paired = FALSE, var.equal = FALSE)$conf
```
The 95 percent confidence interval ( -0.1710156,  7.5710156) include 0. We are not conficent to compare the impacts between OJ and VC supplements.

Compare between dose 0.5 and 1.
```{r}
t.test(tg$len[tg$dose==0.5], tg$len[tg$dose==1], paired = FALSE, var.equal = FALSE)$conf
```
The 95 percent confidence interval ( -11.983781,  -6.276219) does NOT include 0. We are conficent to say it is helpful to tooth length when increasing does from 0.5 to 1.

Compare between dose 1 and 2.
```{r}
t.test(tg$len[tg$dose==1], tg$len[tg$dose==2], paired = FALSE, var.equal = FALSE)$conf
```
The 95 percent confidence interval ( -8.996481, -3.733519) does NOT include 0. We are conficent to say it is helpful to tooth length when increasing does from 1 to 2.

## State your conclusions and the assumptions needed for your conclusions
We can summarize the following.
* We can't find the impact of supplements on tooth length.
* Increasing dose is helpful to tooth length.
We also note that the observation size is still small. More data may help us better understand the impacts.
