---
title: "Statistical Inference Course Project 1"
author: "York Huang"
date: "Sunday, March 13, 2016"
output:
  pdf_document:
    fig_height: 3.5
    toc_depth: 1
---

## Overview

In this project I will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. 

## Prepare Data
Create matrix with 1000 simulations, each has 40 exponential samples.
```{r}
library(knitr)
library(ggplot2)

set.seed(1)
lambda <- 0.2
exps <- matrix( rexp(40*1000, rate=lambda), 1000)

```

## Exploration of Data
Let's calculate the means of each simulations and then draw the histogram.
```{r}
dms <- apply(exps,1, mean)
hist(dms)
```

The summary of means is below.
```{r}
summary(dms)
```

## Sample Mean versus Theoretical Mean
The theoretical mean of the exponential distribution is 1/lambda as below
```{r}
theory_mean = 1 / lambda
print(paste("Theoretical mean = ", 1/lambda))
```

The sample mean is as below.
```{r}
sample_mean = mean(dms)
print(paste("Sample mean = ", sample_mean))

```

The sample mean is very close to theoretical mean.

## Sample Variance versus Theoretical Variance

The theoretical standard deviation is 1/lambda. So the theoretical variance of simulation with n=40 samples is 1/(lambda^2 * n).
```{r}
theoretical_variance = 1 /(lambda^2 * 40)
theoretical_sd = 1/lambda/sqrt(40)
print(paste("theoretical_variance = ", theoretical_variance ))
print(paste("theoretical_deviation = ", theoretical_sd ))

```

The sample variance is as below.
```{r}
sample_variance = var(dms)
sample_sd = sd(dms)
print(paste("sample_variance = ", sample_variance))
print(paste("sample_deviation = ", sample_sd))
```

The sample variance is close to theoretical variance.

## Distribution
In the picture below, the actual exponential distribution and the normal distribution with same mean and deviation are drawn together.

```{r}
dms_frame <- data.frame(dms)
ggplot(dms_frame, aes(x=dms)) + 
  geom_histogram(binwidth=lambda, fill="cyan",color="black",aes(y = ..density..))  +
  stat_function(fun=dnorm, args=list(mean=sample_mean, sd=sample_sd), color = "blue", size = 1.0) +
  geom_vline(xintercept=sample_mean,size=1.0,color="green") 

```

From the picture below, we can see how close is the exponential and normal distributions.
